Masterclass Assignment Documentation

### 2018-01-11 docs/paper/paper.tex
added images to docs

@@

>>>>

\begin{figure}[htbp]\centering
 \includegraphics[width=1.0\linewidth]{images/full_render_01.png}
 \includegraphics[width=1.0\linewidth]{images/full_render_02.png}
 \includegraphics[width=1.0\linewidth]{images/full_render_03.png}
 \caption{\label{fig:reference}Three screenshots showing the full scene with a voxel resolution of 512^3.}
\end{figure}

\begin{figure}[htbp]\centering
 \includegraphics[width=1.0\linewidth]{images/direct_only.png}
 \caption{\label{fig:reference}A screenshot showing just the direct lighting pass.}
\end{figure}

\begin{figure}[htbp]\centering
 \includegraphics[width=1.0\linewidth]{images/indirect_only.png}
 \caption{\label{fig:reference}A screenshot showing just the indirect lighting pass.}
\end{figure}

\begin{figure}[htbp]\centering
 \includegraphics[width=1.0\linewidth]{images/reflection_only.png}
 \caption{\label{fig:reference}A screenshot showing just the reflection pass.}
\end{figure}

\begin{figure}[htbp]\centering
 \includegraphics[width=1.0\linewidth]{images/reflection_only_no_roughness.png}
 \caption{\label{fig:reference}A screenshot showing just the reflection pass, but with the minimum cone angle.}
\end{figure}

@@

\begin{figure}[htbp]\centering
 \includegraphics[width=1.0\linewidth]{images/banding.png}
 \caption{\label{fig:reference}A screenshot showing banding artefacts in the reflection pass.}
\end{figure}

\begin{figure}[htbp]\centering
 \includegraphics[width=1.0\linewidth]{images/indirect_noise.png}
 \caption{\label{fig:reference}A screenshot showing noise in the indirect lighting.}
\end{figure}

\begin{figure}[htbp]\centering
 \includegraphics[width=1.0\linewidth]{images/voxelization_error.png}
 \caption{\label{fig:reference}A screenshot showing voxelization artefacts.}
\end{figure}
